The Unicode Cookbook \linebreak for Linguists

### 2015-10-19 book/chapters/codetesting.tex
some more knitr testing

<<>>=
'this is a simple R example'
test = 3+4
test
@

<<>>=
library(qlcData)
example  = 'AΑА'
profile = write.profile(example)
@

<<Rtest2, tidy = TRUE, results = 'asis', echo = FALSE>>=
library(xtable)
print(xtable(profile, caption = 'test', label = 'bla')
  , include.rownames = FALSE
  , booktabs = TRUE
  , size = 'small'
  , table.placement = 'H'
  )
@

>>>>

<<>>=
'this is a simple R example'

test = 3+4
test
@

<<>>=
library(qlcData) 
profile = write.profile('AΑА')
@

<<Rtest2, tidy = TRUE, results = 'asis', echo = FALSE>>=
print(xtable(profile, caption = 'test', label = 'bla')
  , include.rownames = FALSE
  , booktabs = TRUE
  , size = 'small'
  , table.placement = 'H'
  )
@

### 2015-10-19 book/unicode.tex
some more knitr testing

\definecolor{fgcolor}{rgb}{0, 0, 0}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.502,0,0.502}{\textbf{#1}}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.651,0.522,0}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{1,0.502,0}{#1}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{1,0,0.502}{\textbf{#1}}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.733,0.475,0.467}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.502,0.502,0.753}{\textbf{#1}}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0,0.502,0.753}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0,0.267,0.4}{#1}}%

@@

There is a bug for non-R engines: the fontsize settings are not correct. I have 
filed an issue, hopefully this will be fixed soon.

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.933, 0.933, 0.933}\color{fgcolor}\begin{kframe}
\noindent
\ttfamily
\hlstd{}\hlkwb{echo\ }\hlstd{}\hlstr{'this\ is\ a\ simple\ bash\ example'}\hlstd{}\hspace*{\fill}\\
\hlkwb{echo\ }\hlstd{}\hlstr{'this\ is\ a\ simple\ bash\ example'}\hlstd{}\hspace*{\fill}\\
\hlkwc{ls\ }\hlstd{\textbar \ }\hlkwc{wc}\hlstd{}\hspace*{\fill}
\mbox{}
\normalfont
\normalsize

\begin{verbatim}
## this is a simple bash example
## this is a simple bash example
##       10      10     165
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.933, 0.933, 0.933}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstr{"this is a simple R example"}
\end{alltt}
\begin{verbatim}
## [1] "this is a simple R example"
\end{verbatim}
\begin{alltt}
\hlstd{test} \hlkwb{<-} \hlnum{3} \hlopt{+} \hlnum{4}
\hlstd{test}
\end{alltt}
\begin{verbatim}
## [1] 7
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.933, 0.933, 0.933}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(qlcData)}
\hlstd{example} \hlkwb{<-} \hlstr{"AΑА"}
\hlstd{profile} \hlkwb{<-} \hlkwd{write.profile}\hlstd{(example)}
\end{alltt}
\end{kframe}
\end{knitrout}

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Mon Oct 19 00:52:15 2015
\begin{table}[H]
\centering
{\small
\begin{tabular}{llll}
  \toprule
Grapheme & Frequency & Codepoint & UnicodeName \\ 
  \midrule
A & 1 & U+0041 & LATIN CAPITAL LETTER A \\ 
  Α & 1 & U+0391 & GREEK CAPITAL LETTER ALPHA \\ 
  А & 1 & U+0410 & CYRILLIC CAPITAL LETTER A \\ 
   \bottomrule
\end{tabular}
}
\caption{test} 
\label{bla}
\end{table}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.933, 0.933, 0.933}\color{fgcolor}\begin{kframe}
\noindent
\ttfamily
\hlstd{}\hlkwa{print}\hlstd{}\hlopt{(}\hlstd{}\hlstr{'bla'}\hlstd{\ }\hlopt{+\ }\hlstd{}\hlstr{'bla'}\hlstd{}\hlopt{)}\hspace*{\fill}\\
\hlstd{}\hlkwa{print}\hlstd{}\hlopt{(}\hlstd{}\hlnum{3}\hlstd{}\hlopt{+}\hlstd{}\hlnum{4}\hlstd{}\hlopt{)}\hlstd{}\hspace*{\fill}
\mbox{}
\normalfont
\normalsize

\begin{verbatim}
## blabla
## 7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.933, 0.933, 0.933}\color{fgcolor}\begin{kframe}
\noindent
\ttfamily
\hlstd{}\hlkwa{print}\hlstd{}\hlopt{(}\hlstd{}\hlstr{'python3\ needs\ an\ extra\ tag'}\hlstd{}\hlopt{)}\hspace*{\fill}\\
\hlstd{uni\ }\hlopt{=\ }\hlstd{}\hlstr{'aɽɮz'}\hlstd{}\hspace*{\fill}\\
\hlkwa{print}\hlstd{}\hlopt{(}\hlstd{uni}\hlopt{)}\hlstd{}\hspace*{\fill}
\mbox{}
\normalfont
\normalsize

\begin{verbatim}
## python3 needs an extra tag
## aɽɮz
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

@@

There is a bug for non-R engines: the fontsize settings and line spaceing are not correct. I have 
filed an issue, hopefully this will be fixed soon.

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
echo 'this is a simple bash example'
echo 'this is a simple bash example'
ls | wc
## this is a simple bash example
## this is a simple bash example
##       10      10     165
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
"this is a simple R example"
## [1] "this is a simple R example"

test <- 3 + 4
test
## [1] 7
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
library(qlcData)
example <- "AΑА"
profile <- write.profile(example)
\end{verbatim}
\end{kframe}
\end{knitrout}

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Mon Oct 19 18:08:51 2015
\begin{table}[H]
\centering
{\small
\begin{tabular}{llll}
  \toprule
Grapheme & Frequency & Codepoint & UnicodeName \\ 
  \midrule
A & 1 & U+0041 & LATIN CAPITAL LETTER A \\ 
  Α & 1 & U+0391 & GREEK CAPITAL LETTER ALPHA \\ 
  А & 1 & U+0410 & CYRILLIC CAPITAL LETTER A \\ 
   \bottomrule
\end{tabular}
}
\caption{test} 
\label{bla}
\end{table}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
print('bla' + 'bla')
print(3+4)
## blabla
## 7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
print('python3 needs an extra tag')
uni = 'aɽɮz'
print(uni)
## python3 needs an extra tag
## aɽɮz
\end{verbatim}
\end{kframe}
\end{knitrout}
